Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection

### 2019-05-26 reports/paper1/paper.tex
Grammar check

\begin{abstract}
X-ray computed tomography can be used for defect detection in additive manufacturing. Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features. To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection. A 3D printed sample was manufactured with voids to see if they can be detected. The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test. The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved. Voids with diameters in the order of millimetres were detectable.
\end{abstract}

@@

Quality control in additive manufacturing can be done using x-ray computed tomography (CT) \citep{thompson2016x}. The CT is compared with the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}. The disadvantage of x-ray CT is that it involves the acquisition and reconstruction of thousands of projections of the sample. Speeding up the quality control process on the production line could be done by doing an inspection using a fewer number of projections by sacrificing accuracy \citep{warnett2016towards, brierley2018optimized}.

A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth. This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test. Beforehand however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.

An x-ray projection of a 3D printed sample was obtained and compared with the simulation in an experiment. The procedure is shown in the methods section along with the description of the empirical null filter. In addition, the software development and simulation studies of the filter was discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

An ABS plastic cuboid (\SI{40}{\milli\metre} $\times$ \SI{40}{\milli\metre} $\times$ \SI{60}{\milli\metre}) with voids was purposefully manufactured to see if they can be detected. The CAD shown in Figure \ref{fig:inference_testObject} was manufactured using a \emph{Fortus 400mc (Stratasys, US)} 3D printer. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly. The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$.

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
  \caption{CAD of a 3D cuboid with voids. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly. The scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

@@

The projection of the sample was obtained and repeated 20 times at a fixed angle. The 20 projections were spilt into 2. 19 random projections were held out. The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
CAD of the sample \citep{bellon2011simulation, deresch2012simulating}. \emph{aRTist} was used to obtained a simulation projection as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection. A shading correction was applied to the simulated projection using a flat black image and a simulated white image.

>>>>

\begin{abstract}
X-ray computed tomography can be used for defect detection in additive manufacturing. Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features. To avoid this time-consuming process, it was investigated whenever it is possible to detect defects based on a single angular projection. A 3D printed sample was manufactured with voids to see if they can be detected. The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test. The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved. Voids with diameters in the order of millimetres were detectable.
\end{abstract}

@@

Quality control in additive manufacturing can be done using x-ray computed tomography (CT) \citep{thompson2016x}. The CT is compared with the computer-aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}. The disadvantage of x-ray CT is that it involves the acquisition and reconstruction of thousands of projections of the sample. Speeding up the quality control process on the production line could be done by doing an inspection using a fewer number of projections by sacrificing accuracy \citep{warnett2016towards, brierley2018optimized}.

A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth. This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test. Beforehand, however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.

An x-ray projection of a 3D printed sample was obtained and compared with the simulation in an experiment. The procedure is shown in the methods section along with the description of the empirical null filter. In addition, the software development and simulation studies of the filter were discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

An ABS plastic cuboid (\SI{40}{\milli\metre} $\times$ \SI{40}{\milli\metre} $\times$ \SI{60}{\milli\metre}) with voids was purposefully manufactured to see if they can be detected. The CAD shown in Figure \ref{fig:inference_testObject} was manufactured using a \emph{Fortus 400mc (Stratasys, US)} 3D printer. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise, they were arranged irregularly. The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$.

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
  \caption{The CAD of a 3D cuboid with voids. The voids were of diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise, they were arranged irregularly. The scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

@@

The projection of the sample was obtained and repeated 20 times at a fixed angle. The 20 projections were split into 2. 19 random projections were held out. The remaining projection was used to compare with a simulated projection, obtained using \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \emph{aRTist} can simulate projections of the sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the
CAD of the sample \citep{bellon2011simulation, deresch2012simulating}. \emph{aRTist} was used to obtain a simulation projection as if the voids were not there. Numerical methods were used to align the simulated projection to the obtained projection. A shading correction was applied to the simulated projection using a flat black image and a simulated white image.
